Reanalysis Step 9: Alternative Propensity Score Specifications

### 2025-09-06 reanalysis-9-alternative_specifications.qmd
wip

# Define completed methods (add to this list as methods complete successfully)
completed_methods <- c(
  "nearest_glm"  # Uncomment if completed
)

@@

results <- run_alternative_ps_analysis(
  imputed_datasets = imputed_datasets,
  ps_formula = ps_formula,
  outcome_formula = outcome_formula,
  mode = analysis_mode,
  cache_dir = cache_dir,
  use_cache = use_cache,
  methods_to_run = methods_to_run
)

>>>>

# Define completed methods (add to this list as methods complete successfully)
completed_methods <- c(
  "nearest_glm",  # Completed successfully
  "nearest_gam",  # Completed successfully
  "nearest_gbm",  # Completed successfully
  "nearest_lasso",  # Completed successfully
  "nearest_rpart",  # Completed successfully
  "nearest_mahalanobis",  # Completed successfully
  "subclass_glm",  # Completed successfully
  "cbps",  # Completed successfully
  "entropy",  # Completed successfully
  "bart"  # Completed successfully
  # "twang_gbm"  # Failed - needs rerun after fix
)

@@

results <- run_alternative_ps_analysis(
  imputed_datasets = imputed_datasets,
  ps_formula = ps_formula,
  outcome_formula = outcome_formula,
  mode = analysis_mode,
  cache_dir = cache_dir,
  use_cache = use_cache,
  methods_to_run = methods_to_run,
  all_methods = all_methods  # Pass all methods so completed ones can be loaded from cache
)
